Edge effects and optimal field sizes in Alberta

### 2021-04-30 Manuscript/manuscript.Rmd
Updated figure
Prep for second model run

- Field boundaries were automatically digitized, then manually checked using satellite imagery and classified land cover data 
  - Crop boundaries are flexible, and often change from year to year depending on planting and emergence conditions (e.g. flooding during some years)
  - Additionally, seminatural features often change from year to year
    - Ephemeral wetlands are flooded during some years, but consist mainly of grasses during dry years
    - Grass boundaries can change if fields are used for as haying or pasture during crop rotation
  - This makes accurate and consistent classification of field boundaries very difficult
  - Because of this, we used the following general categories for field boundaries:
    1. Standard: thin ($<10$ m wide) grassy field boundary, often grassy road right-of-ways 
    2. Wetland: permanent wetland, whose borders are largely unchanged from year-to-year
    3. Forest/shrub: permanent windbreaks or remnant forests
    4. Grass: larger grassy area (pasture or permanent seminatural grassland)
    5. Other crop: different crop with little or no visible boundary between planted areas 
    6. Bare: unplanted (fallow), flooded area, or unpaved roads

>>>>

- Field boundaries were automatically digitized, then manually checked using satellite imagery and classified land cover data 
  - Crop boundaries are flexible, and often change from year to year depending on planting and emergence conditions (e.g. flooding during some years)
  - Additionally, seminatural features often change from year to year
    - Ephemeral wetlands are flooded during some years, but consist mainly of grasses during dry years
    - Grass boundaries can change if fields are used for as haying or pasture during crop rotation
  - This makes accurate and consistent classification of field boundaries very difficult
  - Because of this, we define the following general categories for field boundaries:
    1. Standard: grassy field edge, staging yard, or road right-of-way (grassy strip typically 5-10m wide) 
    2. Wetland: permanent wetland, whose borders are largely unchanged from year-to-year
    3. Shelterbelt: permanent windbreaks, shelterbelts, or remnant forests and shrublands
    4. Other crop: annual crop or pasture with little or no visible boundary between planted areas 
    5. Bare: unplanted (fallow), flooded area, staging yard or road with no planted boundary
    6. Grassland: permanent seminatural grassland

    STANDARD
    WETLAND
    SHELTERBELT
    OTHERCROP
    BARE
    GRASSLAND
